Making Sequential Programs Deterministic

### 2019-04-05 experiments.tex
Fix LaTeX error
deflaker togglz

For three of the projects, we could not find the flakiness reported in the
NonDex paper.
\todo{Important: give a sentence description of each one.}
\todo{visualee : Class#getDeclaredMethods}
\todo{easy-batch: Class#getDeclaredFields}
\todo{vraptor : Class#getDeclaredFields}.

@@

\subsection{\TheDeterminismChecker on DeFlaker benchmarks}\label{sec:deflaker-benchmarks}
DeFlaker found 87 previously unknown flaky tests in 93 projects that were being actively developed at the the time
the paper was written. The authors reported 19 of these tests, out of which 7 were addressed by the maintainers of
those projects~\cite{deflaker}.
We ran \theDeterminismChecker on the part of each of these
codebases where the reported bug was fixed, as in \cref{sec:nondex-benchmarks}.
% The DeFlaker authors graciously fixed problems we discovered while using
% their tool.

Two of the seven flaky tests (in \<achilles> and \<jackrabbit-oak>)
were caused by a race condition, which \theDeterminismChecker
cannot detect.  (This is a strength of DeFlaker over \theDeterminismChecker.)
We couldn't find the link to one of the issues in the issue tracker of \<jackrabbit-oak>.
We were unable to build \<tigglz> and \<nutz> which had two and one flakiness issues respectively.
\TheDeterminismChecker was able to find the source of flakiness in \<checkstyle>. This bug was in a test
case that treated an array returned by \<Class.getDeclaredConstructors()>
as deterministic.

>>>>

For three of the projects, we could not find the flakiness reported in the
NonDex paper. The reported root cause of flakiness in \<easy-batch> and
\<vraptor> was a call to \<Class.getDeclaredFields>. We couldn't find a call
to this method in any of the source files of these two repositories.
Similarly, the flakiness in \<visualee> was attributed to an invocation of
\<Class.getDeclaredMethods> which we didn't find in the source code.
%\todo{Important: give a sentence description of each one.}

@@

\subsection{\TheDeterminismChecker on DeFlaker benchmarks}\label{sec:deflaker-benchmarks}
DeFlaker found 87 previously unknown flaky tests in 93 projects that were being actively developed at the time
the paper was written. The authors reported 19 of these tests, out of which 7 were addressed by the maintainers of
those projects~\cite{deflaker}.
We ran \theDeterminismChecker on the part of each of these
codebases where the reported bug was fixed, as in \cref{sec:nondex-benchmarks}.
% The DeFlaker authors graciously fixed problems we discovered while using
% their tool.

Four of the seven flaky tests (two in \<achilles>, one each in \<jackrabbit-oak> and \<togglz>)
were caused by a race condition, which \theDeterminismChecker
cannot detect.  (This is a strength of DeFlaker over \theDeterminismChecker.)
We were unable to build \<togglz> and \<nutz> which had one flakiness issue each.
However, we extracted the source code causing the flakiness in \<togglz> into a test case 
after looking at the issue on Github. This bug was caused by a copy method that iterated over
an \<OrderNonDet Set> and expected it to be deterministic. \TheDeterminismChecker correctly flagged
an error in the loop that iterated over the \<Set>.
\TheDeterminismChecker was able to find the source of flakiness in \<checkstyle>. This bug was in a test
case that treated an array returned by \<Class.getDeclaredConstructors()>
as deterministic.
